%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Bloomberg L.P.} % Organization
    {New York, NY} % Location
    {July 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team as a full stack engineer to support Bloomberg Enterprise Access Point, eap.bloomberg.com. Serves >2M API requests/day. }
        \item {Built multiple backend \cvtag{RestAPI} micro-services using \cvtag{Python}, \cvtag{Flask}, \cvtag{FastApi}, \cvtag{Gunicorn}, \cvtag{Apache Solr} and \cvtag{Apache Kafka} .}
        \item {Created UI components using \cvtag{node}, \cvtag{Express}, \cvtag{TypeScript} and \cvtag{React}.}
        \item {Spearheaded the delivery of various features from technical design, development, deployment to maintenance. }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Research Assistant - Systems Software Research Group (SSRG)} % Job title
    {Virginia Tech} % Organization
    {Blacksburg, VA} % Location
    {August 2017 - May 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked under the supervision of a Research Assistant Professor, this work resulted in a publication in ASPLOS 2022.}
        \item {Improved \cvtag{OS} security by implementing \cvtag{Linux Kernel Module} continuous address space re-randomization to defend against Just-In-Time ROP attacks.}
        \item {Added support to compile and load \cvtag{Linux Drivers} as position independent code, extending KASLR to 64 bits.}
        \item {Implemented lockfree, high performance algorithm for stack and code re-randomizaton.}
        \item {Experiments with ethernet driver re-randomized at 1ms period resulted in negligible  impact on CPU utilization and network throughput. }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Software Engineer - AUTOSAR OS} % Job title
    {Mentor Graphics / Siemens} % Organization
    {Lahore, PK} % Location
    {August 2016 - June 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in a team to implement features and maintain AUTOSAR OS for automotive ECUs. }
        \item {Responsible for maintaining AUTOSAR \cvtag{OS} port on ARM Cortex processors.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Viaesys} % Organization
    {Canada (Remote)} % Location
    {May 2015 - July 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked independently to design and code a hardware gadget for GPS Tracking, Salt Tracking and Field Crew Management for US/Canada for the municipal industry. These devices are operational on the field today. }
        \item {Developed \cvtag{firmware} for ARM® Cortex® M4 μProcessor with fixed-priority preemptive scheduling featuring support for file system and over the air updates. Wrote drivers to interface with various \cvtag{sensors} over a variety of communication protocols.}
        \item {Developed \cvtag{Python} based framework to build, package and deliver over the air updates via TFTP.}
        % \item {Designed circuit schematics, PCB layouts and firmware for embedded IoT devices.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Teaching Assistant - Microcontrollers and Interfacing, Introduction to Programming in C++} % Job title
    {LUMS} % Organization
    {Lahore, PK} % Location
    {Fall, Spring 2014-15} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked under the supervision of a Professor to design development boards that were used in lab exercises and course projects (\textasciitilde 150 pupils).}
        \item {Updated Lab Manuals, delivered lab \cvtag{lectures}, evaluated students’ lab performance and supervised their course projects.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
